Projection variability: Is the family of sentences really a family?

### 2024-02-19 writing/SuB-paper/projection-operators-SuB.tex
SuB paper updates

\section{Introduction} \label{sec:intro}
    The so-called `family of sentences' diagnostic is the standard way of diagnosing whether a content is projective in formal semantics/pragmatics (e.g., \citealt{chierchia_meaning_1990}). For instance, the clausal complement of \emph{discover} is diagnosed as as projective content, if its content (here: that Julian dances salsa) follows not just from \ref{ex:simple}, but also from the variants in \ref{ex:family}, where \ref{ex:simple} is embedded under an entailment-canceling operator, such as negation \ref{ex:neg}, a polar question \ref{ex:q}, an epistemic possibility modal \ref{ex:mod}, or in a conditional antecedent \ref{ex:cond}.

@@

			The mean projection ratings by embedding context and predicate are presented in Figure~\ref{fig:figure4}, which shows that effect of embedding context on projection differs by predicate.

@@

			\begin{figure}[ht]
				\centering
				\includegraphics[width = \linewidth]{mega-veridicality}
				\caption{Mean projection ratings by embedding context and predicate in MegaVeridicality.}
				\label{fig:figure4}
			\end{figure}

@@

The results of the experiments reported on in section \ref{s2} suggest that there is little by-operator projection variation when we aggregate over the clause-embedding predicates and their CCs, but that there is by-operator variation that cannot be neglected when we do not aggregate. These results have two methodological implications. First, when initially investigating the projection of a content (or teaching projection to students), the family-of-sentences can indeed be treated as a family, as standard textbooks assume. However, it is advisable at this step already to apply the diagnostic with all four operators and attend to possible by-operator projection variation.

A second methodological implication of the results of our experiments is that research on projection must consider which entailment-canceling operator to use, and report which entailment-canceling operator was used. This is because the results of the investigation may very well depend on the entailment-canceling operator under which the expressions and contents were embedded. For instance, two contents that exhibit projection variation from under polar questions might not exhibit such differences when embedded under a different entailment-canceling operator, and two contents that do not exhibit projection variation when embedded under negation, might exhibit variation when embedded under a different entailment-canceling operator.

@@

In this section, we consider whether contemporary analyses can capture the observed by-predicate projection variation and the interactions between predicate and entailment-canceling operator in projection ratings. 
%We consider three types of analyses: (i) analyses that assume that the CCs of factive predicates are lexically specified as presupposed  (\citealt{heim_projection_1983,van_der_sandt_presupposition_1992}), (ii) analyses on which backgrounded entailments are projective (\citealt{abrusan_predicting_2011,simons_best_2017}), and (iii) an analysis on which contextual entailments are presupposed 
%with a triggering algorithm based on world-knowledge that operates over contextual entailments of an utterance 
%(\citealt{schlenker_triggering_2021}).

%While all of these approaches meet limitations in accounting for our data, we argue that the observed gradient effects of predicate/operator interactions favor integrating insights from competing accounts, namely a contextual triggering algorithm (as in \citealt{abrusan_predicting_2011,simons_best_2017}) operating over contextual set of inferences (as in \citealt{schlenker_triggering_2021}).

	%Our results---that projection is modulated by entailment-canceling operators and that there is by-predicate variation in the effect of operator on projection---are not captured by contemporary projection analyses.

@@

These analyses do not predict the observed by-predicate variation, for several reasons. One reason is that there is variation between the factive predicates: For instance, the CC of \emph{be annoyed} is more projective than that of \emph{discover}, which in turn is more projective than that of \emph{reveal}. This variation is not predicted because the CCs of factive predicates are invariably specified as presupposed, with no mechanism to predict projection variation between factive predicates. (Recourse to local accommodation is not possible because the stimuli in our experiments were presented in minimal contexts that were not inconsistent with the CCs.)  A second reason is that the CCs of some non-factives predicates (e.g., \emph{inform, acknowledge})  are just as projective as those of some factive predicates, or even more projective. Analyses like those in \citealt{heim_projection_1983} and \citealt{van_der_sandt_presupposition_1992} fail to make predictions about the projection of the CCs of non-factives predicates. Thus, as discussed in detail in \citealt{degen_are_2022}, the factive/non-factive distinction is not sufficiently fine-grained to adequately predict the observed by-predicate projection variation.

%The assumption of categorical lexical triggering does not address the projection variation among purported factive predicates (see also discussion in \citealt{degen_are_2022}). It also cannot address the fact that the CCs of some non-factive predicates (e.g., \emph{inform, acknowledge}) project just as much, or more, than some (semi-)factive predicates (e.g., \emph{reveal, discover, see}). That is because, it only makes predictions for the projection of the CC of (semi-)factive predicates, whose CCs are analyzed as presuppositions. It therefore does not address the data for the non-veridical predicates in our study.
		%
%		Further, the categorical lexical distinctions are not sufficiently fine-grained to make predictions about the gradient by-predicate variation in the effect of operator on projection.
		%
%		This interaction effect can only be addressed by taking into account more fine-grained lexical distinctions than assuming that some predicates are presuppositional, while others are not.

        %In our experiment, the stimulus utterances were presented out of the blue, leaving it to the participants to imagine a suitable discourse context. Therefore, none of the CCs should be interpreted as necessarily inconsistent with contextual information.
		%
		The analyses in \citealt{heim_projection_1983} and \citealt{van_der_sandt_presupposition_1992} also do not predict differential effects of entailment-cancelling operators on projection. This is because negation and conditional antecedents are given a semantics that derives their behavior as presuppositional holes, in the sense of \citealt{karttunen_observations_1971}. For instance in \citealt{heim_projection_1983}, presupposition triggers under negation or in conditional antecedents are evaluated relative to the global context, with the consequence that presuppositions are not expected to differentially project from under negation or conditional antecedents. %Therefore, presupposition triggers under these operators are predicted to behave like unembedded ones, with no expected differences. 
  While the analysis does not explicitly address epistemic possibility modals or polar questions, we might expect that they would be treated as presuppositional holes along the same lines, therefore also not predicting any by-operator projection variation, by by-predicate variation in the effect of entailment-canceling operators.
		%
		%Differential effects of operators on projection could conceivably be addressed in such a system by assuming that the meaning of entailment-cancelling operators systematically affects the possibility of local accommodation (e.g., by assuming that accommodation is more likely under modals than conditional antecedents). However, no such effects have been spelled out.

@@

\citealt{abrusan_predicting_2011} and \citealt{simons_best_2017} do not assume that presuppositions are lexically specified. In \citealt{abrusan_predicting_2011}, a lexical entailment of an uttered sentence is a presupposition if it is about a time that is not the event time of the matrix predication and it is not at-issue with respect to the Question Under Discussion (QUD, see \citealt{roberts_information_1996,roberts_information_2012}) addressed by the utterance. For instance, the CC of B's utterance in \ref{ent}, that Phil's ballet class is canceled, is predicted to be a presupposition (and therefore to project) because it is a lexical entailment of the sentence embedded under the epistemic modal and not at-issue with respect to A's interrogative utterance.

@@

In \citealt{simons_best_2017}, the CC of a clause-embedding predicate projects if it is entailed by the Current Question of the utterance (where the Current Question is the question that is congruent with the utterance).\footnote{The Current Question is defined in \citealt[194]{simons_best_2017} as follows: ``The Current Question for an utterance is a privileged subset of the focal alternative set of the uttered sentence (given a structural analysis of that sentence, including focus marking)'' which meets the conditions that ``i) the proposition expressed is a member of the Current Question and ii) the Current Question has at least one additional member.''} In \ref{ent},  the Current Question of B's utterance might be the set of propositions \{Phil forgot that his ballet class is canceled today, Phil is aware that his ballet class is canceled today\}. If so, the Current Question entails that Phil's ballet class is canceled today, and the CC may therefore project under \poscite{simons_best_2017} analysis.

%assume that projection is not determined lexically, but by a triggering mechanism, which operates over the entailments of an expression, and determines which of them projects. They assume entailments project that do not contribute to the main point invoked by the utterance.
		% Instead of assuming that the possibility of projection is determined lexically, the accounts in \cite{abrusan_predicting_2011,simons_best_2017} and \citet{schlenker_triggering_2021} assume a triggering mechanism, which operates over a set of inferences associated with an utterance, and determines which of them projects. The assumed triggering mechanisms differ on two dimensions: (i) how the set of inferences is determined that constitutes the input to the triggering mechanism, and (ii) the algorithm by which these inferences are derived as projective or not.

		%
		%In such analyses, every utterance addresses a question, which is determined by its alternative-structure, which, can be indicated by focus-marking. For example, in a modalized utterance with \emph{be annoyed}, the CC can be focused \Next[b], which leads to the alternative structure in \Next[c], allowing the utterance to address a question like \Next[a].

@@

		%The account assumes that an inference projects if it is entailed by the union of the alternatives (see also \citealt{abusch_presupposition_2010}). therefore predicting projection of the CC in \Last, but not \LLast. That is, under the assumption that $x$ \emph{was annoyed that} $p$ entails $p$.

Like the analyses discussed in the previous section, the analyses in \citealt{abrusan_predicting_2011} and \citealt{simons_best_2017} do not predict the observed by-predicate variation. First, if the CCs of factive predicates are entailed, they are invariably predicted to project, and so the observed differences between the CCs of different factive predicates are not predicted.  Second, the analyses do not make predictions for non-entailed CCs, and hence they do not predict that the CCs of some non-factives predicates project at least as much or even more than those of some factive predicates. Neither of the analyses makes predictions about by-operator projection variation, nor about by-predicate variation in the effect of entailment-canceling operators.

%  The triggering mechanisms assumed in \citealt{abrusan_predicting_2011} and \citealt{simons_best_2017}, predict a potential of projection for inferences that are entailed by the literal content of the modal prejacent $p$ in \Last and \LLast, and similarly for propositions embedded under negation, and in conditional antecedents or polar questions. These accounts, therefore, predict a potential of projection for CCs that are entailed by the prejacent, due to the lexical entailments of veridical predicates, or due to entailments that are contributed compositionally by the literal content (see e.g., \citealt{roberts_i_2019}). However, they do not make systematic predictions for CCs, such as in \Last, that are not entailed. As a result, these accounts cannot address the fact that we see some amount of projection for all of the tested predicates.

		%Because the main point of an utterance is often determined in the discourse context (\citealt{roberts_information_1996,roberts_information_2012}, \emph{et seq.}), these approaches incorporate discourse effects on projection.
		%
		% \citet{abrusan_predicting_2011} also makes predictions for utterances in out-of-the-blue contexts: Utterances are associated with a default main point that is grammatically determined by the time at which the matrix predicate is interpreted.
		%
		%The account in \citealt{simons_best_2017} could be extended to address our gradient data in out-of-the blue contexts, by assuming (i) that embedded contents that are not at-issue can project even if they are not entailed, and (ii) that linguistic expressions differ in how likely the contributed contents are interpreted as at-issue (as suggested in \citealt{tonhauser_how_2018}).
		%
		%In our data, for instance, the CC of \emph{discover} \Next[a] has received relatively high projection ratings, while that of \emph{confirm} \Next[b] has received medium to low ratings. To explain this difference, the information-structure based triggering approach would need to assume that the CC of \emph{discover} is less likely to be at issue than that of \emph{confirm}.

	%	\ex. \a. Perhaps Cole discovered that Julian dances salsa.
	%		\b. Perhaps Cole confirmed that Julian dances salsa.
%			\z.
%		\z.

		%While \citet{tonhauser_how_2018} experimental evidence that projection ratings negatively correlate with at-issueness ratings in out-of-the-blue polar questions. \citet{sieker_projective_2022} argue that their data also shows the same correlation for modals, conditional antecedents, and negation for the German clause-embedding predicates they investigated. To address the gradient by-predicate variation theoretically, this approach would need to explicitly spell out how various predicates are associated with different likelihoods that their CCs is interpreted as at-issue.

		%\paragraph{By-operator variation.} Neither of the analyses make predictions about by-operator variation.
			%Since we found an operator/predicate interaction effect on projection, a further prediction of this type of approach would be that at-issueness ratings would show an operator-predicate interaction in this experimental setup as well. To address the interaction effect theoretically, an information structural triggering approach would need to make explicit predictions about how the meaning of entailment-cancelling operators affects at-issueness differentially for different predicates. This is certainly conceivable, when we take default assumptions about how likely embedded contents are interpreted at issue to be associated with the entire embedding context, including clause-embedding predicates, but also entailment-cancelling operators. However, this has not been spelled out explicitly and needs to be investigated in more detail.

@@

On the analysis proposed in \citealt{schlenker_triggering_2021}, the CC of a sentence S, like \ref{knowa}, that is uttered in a context $c$ is presupposed if the CC is presupposed by the sentence S$'$under the entailment-canceling operator, that is \ref{knowb}, in the local context $c'$. For the CC to be presupposed in \ref{knowb}, two conditions must be met: i) S$'$ contextually entails the CC relative to $c'$; and ii) If we consider ``a generic agent'' who believes the propositions in $c'$ and who has now learned about the truth of S$'$, then the probability that this generic agent already believed the CC is above a contextual threshold $\alpha$ (\S6.2); more colloquially, condition ii) requires that the generic agent ``typically antecedently believes'' the CC (p.6) upon interpreting S$'$ in $c'$. Applied to \ref{know}, \poscite{schlenker_triggering_2021} analysis predicts that the CC  is presupposed if i) \ref{knowb} contextually entails that Julian dances salsa, and ii) if a generic agent would typically antecedently believe that Julian dances salsa upon interpreting \ref{knowb} in the minimal contexts we provided to our participants. (For \citealt{schlenker_triggering_2021}, the local context under negation $c'$ is identical to $c$.)

@@

Condition i) is met under the assumption that the CC of \ref{knowb} is an entailment. \citealt{schlenker_triggering_2021} also assumes the condition ii) is met: ``in many cases, one's knowledge of facts will precede one's knowledge of [Cole's] beliefs about them\ldots believing that [Julian dances salsa] is often an epistemic precondition for believing that'' Cole knows that Julian dances salsa (p.6). One might, however, challenge this assumption on the basis of the corpus study presented in \citealt{spenader02}, which showed that the CCs of the majority of the utterances of sentences with factive verbs (namely 81 out of 109) had to be accommodated (i.e., were not contextually entailed). In other words, utterance of sentences with the factive predicates investigated by \citet{spenader02}, which included \emph{know}, were ``generally used to communicate information the speaker thought was hearer-new'' (p.99). This result might therefore suggest that one cannot assume that a generic agent typically antecedently believes the CC of {\em know}.

We assume that it is an open, empirical question which predicates are such that the probability of a generic agent antecedently believing the CC is above the contextual threshold $\alpha$ in the minimal contexts we provided our participants (and, of course, what that threshold might be). \citealt{schlenker_triggering_2021} appears to assume that there are two classes of predicates: those where the probability is above the threshold (including {\em know, inform}, and {\em announce}), and those where it is not (including {\em demonstrate} and {\em establish}; see p.12 and appendix I). Thus, one advantage of \poscite{schlenker_triggering_2021} analysis over the analyses reviewed in sections \ref{s:heim} and \ref{s:abrusan} is that it is able to predict the projection of the CCs of non-factives predicates (modulo the open questions about condition ii)).

Does \poscite{schlenker_triggering_2021} analysis capture the observed by-predicate variation? The analysis correctly predicts that the CCs of \emph{know, inform}, and \emph{announce} are more projective than the CCs of \emph{demonstrate} and \emph{establish}, by virtue of the CCs of the former being possibly presupposed, in contrast to the CCs of the latter. It is not clear, however, that the analysis is able to predict the observed variation because the analysis -- even  though it does not divide predicates into factive and non-factives ones -- nevertheless suggests a binary, categorical distinction between predicates, such that the CCs of predicates with probabilities above the threshold may be presupposed (depending on the context), and those below the threshold are not. First, as shown in Figs.~\ref{fig:op-pred-ratings} and \ref{fig:op-pred-ratings2}, and discussed extensively in \citealt{degen_are_2022}, there is projection variation between the supposedly presupposed CCs that is not captured by an analysis that does not make more fine-grained distinctions between the meanings of clause-embedding predicates. Furthermore, it is not clear that the supposedly nonpresupposed CCs are not projective. Second, as discussed in \citealt{degen_are_2022}, the CCs of non-factives predicates like \emph{establish} and \emph{demonstrate} are projective when compared to nonprojective main clause content. \poscite{schlenker_triggering_2021} analysis does not make predictions for these CCs. In the experiments reported on in section \ref{s2}, the mean certainty rating of the CC of \emph{announce}, whose CC is assumed to possibly be presupposed, is .XX, and that of {\em demonstrate}, whose CC is not assumed to be presupposed, is .XX (both means are aggregated across entailment-canceling operators). It is not clear whether this particular difference in mean certainty rating motivates analyzing the CC of \emph{announce} as presupposed in contrast to that of \emph{demonstrate}.

%The triggering mechanism assumed in \citealt{schlenker_triggering_2021} operates on local contextual entailments of an expression, and determines which one of them projects based on probabilistic world knowledge about the truth of the invoked contents. For instance, the CC of the utterance with \emph{discover} in \Next[a], that Julian dances salsa, has the potential to project if it is entailed by the sentence in the scope of negation (namely \Next[b]) together with information that is available in its local context. Negation is treated as a presuppositional hole, and the local context under negation is taken to be the global context (as in  \citealt{heim_projection_1983} and \citealt{schlenker_local_2009}).

	%		\ex. \a. Cole didn't discover that Julian dances salsa.
	%			\b. Cole discovered that Julian dances salsa.
	%		\z.

			%The triggering mechanism states that an inference $p$ of some propositional expression $E$ pro\-jects if $p$ is an epistemic precondition for the truth of $E$ in its local context $c^\prime$. So, the CC of \Last[a] projects if the CC is an epistemic precondition for the truth of \Last[b].
			%
			%$p$ is an epistemic precondition of $E$ in $c^\prime$ if, usually, when one acquires the belief in $c^\prime$ that $E$, one already knows that $p$. 
			%
			%The CC of \Last[a] can be taken to be an epistemic precondition for \Last[b] based on the \lq subjective conditional probability\rq\ that a generic epistemic agent would already believe that Julian dances salsa when learning that \Last[b] is true. Specifically, the CC is taken to be an epistemic precondition if that probability reaches a contextually given threshold.

%   In order to extend an account along these lines to address the out-of-the-blue utterances in our experiment, we might assume that these utterances are interpreted relative to an imagined plausible discourse context (for discussion, see \citealt{simons_best_2017}).

   %It can therefore incorporate effects of contextual information on projection, such as the reliability of the source of a speech report (\citealt{rieh_credibility_2010,de_marneffe_did_2012}).

%Due to the probabilistic nature and context-sensitivity of the triggering mechanism, the approach can make gradient predictions. However, the subjective conditional probabilities associated with expressions and their contextual inferences are taken as given in the account. In order to make concrete predictions about the gradient by-predicate variation, this account would need to make explicit how the relevant probabilities are derived based on different predicates. For instance, to explain the contrast that \emph{discover} receives higher projection ratings than \emph{confirm}, this account would assume that the situations in which one learns that a sentence like \emph{$x$ discovered that $p$} is true, are such that one already knew that $p$ is true more often than situations in which one learns the truth of a sentence like \emph{$x$ confirmed that $p$}.

\poscite{schlenker_triggering_2021} analysis does not incorporate differential effects of entailment-cancelling operators on projection. For instance, the local contexts $c'$ under negation and in conditional antecedents are both assumed to be the global context $c$ (based on \citealt{heim_projection_1983,schlenker_local_2009}). Therefore, the analysis does not make predictions about by-operator projection variation or about by-predicate variation in the effect of entailment-canceling operator.

%For instance, the conditional probability for $p$ given $E$ vs.\ that of $p$ given $(\emph{not } E)$ or that of $p$ given $(\emph{if } p, q)$ should not differ.

%			In order to address the operator-predicate interaction effect, an approach based on epistemic preconditions would need to make explicit how the meaning of entailment-cancelling operators affects the conditional probabilities differentially for different predicates.
			%
%			The conditional probability that some embedded content is antecedently known would need to be computed relative to a global context, and take into account the entire embedding context, including the combination of entailment-cancelling operator and clause embedding predicate.

@@

There is currently no projection analysis on the market that predicts the by-predicate and by-operator variation we observed in the experiments reported on in section \ref{s2}. \citealt[585]{degen_are_2022} suggested that an empirically adequate analysis to capture the observed by-predicate variation requires consideration of ``more fine-grained distinctions [between clause-embedding predicates] that are based on the lexical meaning and discourse use of clause-embedding predicates''. In the next section, we offer some hypotheses based on the data from our experiments.

%	\subsubsection{Discussion: Contextual inferences and probabilistic triggering}

%		Our data showed gradient projection variation, based on a main effect of predicate, and an operator-predicate interaction. We found these effects for the CCs of clause-embedding predicates under four entailment-cancelling operators in out-of-the-blue contexts. The fact that we see some amount of projection for all predicates (even non-veridical ones), can only be addressed by an account that assumes the potential of projection for contextual inferences, rather than only literal ones.

%		The main effect of predicate and the operator-predicate interaction are both gradient effects, and cannot be explained by a categorical distinction between presuppositional and non-pre\-suppo\-si\-tion\-al predicates. The effects could rather be addressed in a probabilistic account, where various embedding contexts (i.e., combinations of entailment-cancelling operator and predicate) are associated with different probabilities that the embedded content projects.

%		Under the assumption of information-structural triggering, this is the probability that the embedded content is not at issue in the (possibly imagined) discourse context. Under a world-knowledge-based triggering account, the projection probability can be associated with the probability that the embedded content is already known in the discourse context. These two notions are, of course, related. If some proposition is already known, raising an issue about whether $p$ is the case will be uninformative. Therefore, it is unclear whether these two approaches would make different predictions for our data. Both types of accounts would need to be extended to make concrete predictions for the contribution of the combinations of entailment-cancelling operators and predicates.

>>>>

\section{Introduction} \label{sec:intro}
    The so-called `family of sentences' diagnostic is the standard way of diagnosing whether a content is projective in formal semantics/pragmatics (e.g., \citealt{chierchia_meaning_1990}). For instance, the clausal complement of \emph{discover} is diagnosed as projective content, if its content (here: that Julian dances salsa) follows not just from \ref{ex:simple}, but also from the variants in \ref{ex:family}, where \ref{ex:simple} is embedded under an entailment-canceling operator, such as negation \ref{ex:neg}, a polar question \ref{ex:q}, an epistemic possibility modal \ref{ex:mod}, or in a conditional antecedent \ref{ex:cond}.

@@

	The mean projection ratings by embedding context and predicate are presented in Figure~\ref{fig:megaverid}, which shows that effect of embedding context on projection differs by predicate.

@@

			\begin{figure}[ht]
				\centering
				\includegraphics[width = \linewidth]{megaveridicality}
				\caption{Mean projection ratings by embedding context and predicate in MegaVeridicality.}
				\label{fig:megaverid}
			\end{figure}

@@

    The results of the experiments reported on in section \ref{s2} suggest that there is little by-operator projection variation when aggregating observations for the CCs of the  clause-embedding predicates, but that there is by-operator variation that cannot be neglected when we do not aggregate. These results have two methodological implications. First, when initially investigating the projection of a content (or teaching projection to students), the family-of-sentences can indeed be treated as a family, as standard textbooks assume. However, it is advisable to apply the diagnostic with all four operators and attend to possible by-operator projection variation.

	A second methodological implication of the results of our experiments is that research on projection should take into account possible by-operator variation when choosing which entail\-ment-canceling operator to use. Further, results about projection variation should be relativized to the entailment-canceling operator under which the expressions and contents were embedded, as they may very well depend on this choice. For instance, two contents that exhibit projection variation when embedded under polar questions might not exhibit such differences from under a different entailment-canceling operator, and two contents that do not exhibit different projection across negation might exhibit variation when embedded under some other operator.

@@

    This section discusses whether contemporary analyses can capture the observed by-predicate projection variation and the interactions between predicate and entailment-canceling operator in projection ratings. 
	% Our results---that projection is modulated by entailment-canceling operators and that there is by-predicate variation in the effect of operator on projection---are not captured by contemporary projection analyses.

@@

    These analyses do not predict the observed by-predicate variation, for several reasons. One reason is  variation among the factive predicates: For instance, when embedded under polar questions, negation, or \emph{perhaps,} the CC of \emph{be annoyed} is more projective than that of \emph{discover}, which in turn is more projective than that of \emph{reveal}. (In conditional antecedents, the order of \emph{be annoyed} and \emph{discover} is reversed, see Figure~\ref{fig:op-pred-ratings2}).
    %
    This variation is not predicted because the CCs of factive predicates are invariably specified as presupposed, with no mechanism to predict projection variation between factive predicates. (Recourse to local accommodation is not possible because the stimuli in our experiments were presented in minimal contexts that were not inconsistent with the CCs.)  A second reason is that the CCs of some non-factives predicates (e.g., \emph{inform, acknowledge}) are just as projective as those of some factive predicates, or even more projective. Analyses like those in \citealt{heim_projection_1983} and \citealt{van_der_sandt_presupposition_1992} fail to make predictions about the projection of the CCs of non-factives predicates. Thus, as discussed in detail in \citealt{degen_are_2022}, the factive/non-factive distinction is not sufficiently fine-grained to adequately predict the observed by-predicate projection variation.

    The analyses in \citealt{heim_projection_1983} and \citealt{van_der_sandt_presupposition_1992} also do not predict differential effects of entailment-cancelling operators on projection. This is because negation and conditional antecedents are given a semantics that derives their behavior as presuppositional holes, in the sense of \citealt{karttunen_observations_1971}. For instance in \citealt{heim_projection_1983}, presupposition triggers under negation or in conditional antecedents are evaluated relative to a local context that is equal to the global context, with the consequence that presuppositions are not expected to project differently from under negation or conditional antecedents. While the analysis does not explicitly address epistemic possibility modals or polar questions, we might expect that they would be treated as presuppositional holes along the same lines, therefore also not predicting any by-operator projection variation, or by-predicate variation in the effect of entailment-canceling operators.
	%
	%Differential effects of operators on projection could conceivably be addressed in such a system by assuming that the meaning of entailment-cancelling operators systematically affects the possibility of local accommodation (e.g., by assuming that accommodation is more likely under modals than conditional antecedents). However, no such effects have been spelled out.

@@

    \citealt{abrusan_predicting_2011} and \citealt{simons_best_2017} do not assume that presuppositions are lexically specified. In \citealt{abrusan_predicting_2011}, a lexical entailment of a (possibly embedded) sentence is a presupposition, if it is about a time that is not the event time of the matrix predication and it is not at-issue with respect to the Question Under Discussion (QUD, see \citealt{roberts_information_1996,roberts_information_2012}) addressed by the utterance. For instance, the CC of B's utterance in \ref{ent}, that Phil's ballet class is canceled, is predicted to be a presupposition (and therefore to project) because it is a lexical entailment of the modal prejacent and not at-issue with respect to A's interrogative utterance.

@@

    In \citealt{simons_best_2017}, the CC of a clause-embedding predicate projects if it is entailed by the Current Question of the utterance (where the Current Question is the question that is congruent with the utterance).\footnote{The Current Question is defined in \citealt[194]{simons_best_2017} as follows: ``The Current Question for an utterance is a privileged subset of the focal alternative set of the uttered sentence (given a structural analysis of that sentence, including focus marking)'' which meets the conditions that ``i) the proposition expressed is a member of the Current Question and ii) the Current Question has at least one additional member.''} In \ref{ent},  the Current Question of B's utterance might be the set of propositions \{Phil forgot that his ballet class is canceled today, Phil is aware that his ballet class is canceled today\}. If so, the Current Question entails that Phil's ballet class is canceled today, and the CC may therefore project under \poscite{simons_best_2017} analysis.
		%
		%In such analyses, every utterance addresses a question, which is determined by its alternative-structure, which, can be indicated by focus-marking. For example, in a modalized utterance with \emph{be annoyed}, the CC can be focused \Next[b], which leads to the alternative structure in \Next[c], allowing the utterance to address a question like \Next[a].

@@

    Under the analyses in \citealt{abrusan_predicting_2011} and \citealt{simons_best_2017}, CCs that are entailed based on the literal content of an utterance may or may not project, depending on whether they contribute to the main point of the utterance. This opens up the possibility for projection variation among veridical predicates (including those often characterized as factive), representing an improvement compared to the lexical specification of factivity assumed in \citealt{heim_projection_1983} and \citealt{van_der_sandt_presupposition_1992}. However, these accounts still do not predict the observed by-predicate variation.
    %
    First, to make explicit predictions about the observed by-predicate variation, these types of analyses would need to make explicit assumptions about how different predicates contribute to how the question under discussion is chosen.
    %
    % The analyses in \citealt{abrusan_predicting_2011} and \citealt{simons_best_2017} do not predict the observed by-predicate variation. First, if the CCs of factive predicates are entailed, they are invariably predicted to project, and so the observed differences between the CCs of different factive predicates are not predicted.
    %
    Second, the analyses do not make systematic predictions for non-entailed CCs, and hence they do not predict that the CCs of some non-factives predicates project at least as much or even more than those of some factive predicates.

    Both of these analyses set aside the effect of entailment-cancelling operators in determining the main point of an utterance. Therefore they do not make predictions about by-operator differences or by-predicate variation in the effect of entailment-canceling operators.

@@

    Under the view put forward in \citealt{schlenker_triggering_2021}, the CC of a sentence $S$ like \ref{knowa}, is presupposed in a context $c$, if the CC is an epistemic precondition on the global meaning of $S$. Formally, Schlenker defines presuppositions relative to their local context (\S6.2). For instance, in \ref{knowa}, the negative prejacent $S'$, that is \ref{knowb}, is presupposed in the local context under negation $c'$, if two conditions are met:
	i) $S'$ contextually entails the CC relative to $c'$;
	and ii) If we consider ``a generic agent'' who believes the propositions in $c'$ and who has now learned about the truth of S$'$, then the probability that this generic agent already believed the CC is above a contextual threshold $\alpha$;
	more colloquially, condition ii) requires that the generic agent ``typically antecedently believes'' the CC (p.6) upon interpreting S$'$ in $c'$. Based on \citealt{heim_projection_1983} and \citealt{schlenker_local_2009}, the the local context under negation $c'$ is assumed to be identical to the global context $c$. Therefore, epistemic preconditions relative to $c'$ will also apply to the global context.

	Applied to \ref{know}, \poscite{schlenker_triggering_2021} analysis predicts that the CC  is presupposed if i) \ref{knowb} contextually entails that Julian dances salsa, and ii) if a generic agent would typically antecedently believe that Julian dances salsa upon interpreting \ref{knowb} in the minimal contexts we provided to our participants.

@@

	Condition i) is met under the assumption that the CC of \ref{knowb} is an entailment. \citealt{schlenker_triggering_2021} also assumes the condition ii) is met: ``in many cases, one's knowledge of facts will precede one's knowledge of [Cole's] beliefs about them\ldots believing that [Julian dances salsa] is often an epistemic precondition for believing that'' Cole knows that Julian dances salsa (p.6). One might, however, challenge this assumption on the basis of the corpus study presented in \citealt{spenader_presuppositions_2002}, which showed that the CCs of the majority of the utterances of sentences with factive verbs (namely 81 out of 109) had to be accommodated (i.e., were not contextually entailed). In other words, utterance of sentences with the factive predicates investigated by \citet{spenader_presuppositions_2002}, which included \emph{know}, were ``generally used to communicate information the speaker thought was hearer-new'' (p.99). This result might therefore suggest that one cannot assume that a generic agent typically antecedently believes the CC of {\em know}.

    \poscite{schlenker_triggering_2021} analysis does not incorporate differential effects of entailment-cancelling operators on projection. As discussed for \citealt{heim_projection_1983}, above, the local contexts under negation and in conditional antecedents are both assumed to be the global context (and similarly in \citealt{schlenker_local_2009}). Therefore, the analysis does not make predictions about by-operator projection variation or about by-predicate variation in the effect of entailment-canceling operator.

    Does the account capture the observed by-predicate variation?
    %
    Because the probabilities about previous beliefs and the threshold $\alpha$ are assumed to potentially vary based on the context, the formal proposal does not in principle preclude the possibility of by-predicate projection variation. However, the subjective conditional probabilities associated with expressions and the contextual threshold $\alpha$ are taken as given in the account, and therefore do not offer explicit or systematic predictions about projection ratings for different expressions.
    %
    We, therefore, assume that it is an open, empirical question which predicates are such that the probability of a generic agent antecedently believing the CC is above the contextual threshold $\alpha$ in the minimal contexts we provided our participants (and, of course, what that threshold might be).

    Throughout the discussion, however, \citealt{schlenker_triggering_2021} appears to assume that there are two classes of predicates: those where the probability is usually above the threshold (including {\em know, inform}, and {\em announce}), and those where it is not (including {\em demonstrate} and {\em establish}; see p.12 and appendix I).
    %
    As this division does not fall along the lines of traditionally assumed classes of (non-)factives,
    % Thus,
    one advantage of \poscite{schlenker_triggering_2021} analysis over the analyses reviewed in sections \ref{s:heim} and \ref{s:abrusan} is that it predicts the projection of the CCs of (certain) non-factive predicates (modulo the open questions about condition ii)).

    Based on these assumptions, the analysis correctly predicts that the CCs of \emph{know, inform}, and \emph{announce} are more projective than the CCs of \emph{demonstrate} and \emph{establish}, by virtue of the CCs of the former being usually presupposed, in contrast to the CCs of the latter. It is not clear, however, that the analysis is able to predict the observed variation, because the analysis -- even  though it does not divide predicates into factive and non-factives ones -- nevertheless imposes a binary, categorical distinction between predicates.
    % such that the CCs of predicates with probabilities that are usually above the threshold are presupposed, and those below the threshold are not.
    %
    Crucially, the by-predicate variation reported in Sections \ref{s:by-pred}+\ref{s:factivity} is not captured by an analysis that does not make more fine-grained distinctions between the meanings of clause-embedding predicates, as discussed extensively in \citealt{degen_are_2022}. First, there is projection variation between the supposedly presupposed CCs (that of \emph{know} is more projective than the CC of \emph{inform}, which is more projective than that of \emph{announce}, under all four operators).
    %
    Furthermore, as discussed in \citealt{degen_are_2022}, the CCs of the supposedly nonpresupposed CCs (of \emph{establish} and \emph{demonstrate}) are projective when compared to nonprojective main clause content. In the experiments reported on in section \ref{s2}, the mean certainty rating of the CC of \emph{announce}, whose CC is assumed to possibly be presupposed, is $0.55$, and that of {\em demonstrate}, whose CC is not assumed to be presupposed, is $0.43$ (both means are aggregated across entailment-canceling operators). It is not clear whether this particular difference in mean certainty rating motivates analyzing the CC of \emph{announce} as presupposed in contrast to that of \emph{demonstrate}.

@@

    There is currently no projection analysis on the market that predicts the by-predicate and by-operator variation we observed in the experiments reported on in section \ref{s2}. \citealt{degen_are_2022} suggested that an empirically adequate analysis to capture the observed by-predicate variation requires consideration of ``more fine-grained distinctions [between clause-embedding predicates] that are based on the lexical meaning and discourse use of clause-embedding predicates'' (p.~585). Further, an account of the observed by-predicate variation in the effects of entailment-cancelling operators will need to take into account how semantic and pragmatic properties of predicate meanings interact with entailment-cancelling operators in varying ways. In the next section, we offer some hypotheses based on the data from our experiments.
